### 2015-08-06 output/table_compare_classalg.tex
Add manual to dictionary

\begin{table}
\begin{small}
\begin{threeparttable}
\caption{{\normalsize Evaluation of different classification algorithms}}
\label{table:table_compare_classalg}
\begin{tabular}{rllllllllll}
\toprule 
 & \textbf{automat} & \textbf{robot} & \textbf{movable arm} & \textbf{algorithm} & \textbf{manual} & \textbf{software} & \textbf{computer} & \textbf{program} & \textbf{digital} & \textbf{autonomous}  \tabularnewline 
\midrule 
Accuracy & 0.79 & 0.76 & 0.76 & 0.78 & 0.71 & 0.77 & 0.76 & 0.72 & 0.76 & 0.77  \tabularnewline 
Precision & 0.56 & 0.75 & 0.33 & 0.63 & 0.37 & 0.53 & 0.49 & 0.40 & 0.49 & 1.00  \tabularnewline 
Recall & 0.56 & 0.03 & 0.01 & 0.19 & 0.27 & 0.22 & 0.36 & 0.30 & 0.35 & 0.03  \tabularnewline 
F-measure & 0.56 & 0.06 & 0.02 & 0.29 & 0.31 & 0.31 & 0.42 & 0.34 & 0.41 & 0.06  \tabularnewline 
AUC & 0.71 & 0.51 & 0.50 & 0.58 & 0.56 & 0.58 & 0.62 & 0.58 & 0.62 & 0.51  \tabularnewline 
Matthew's C.C. & 0.42 & 0.11 & 0.02 & 0.25 & 0.14 & 0.23 & 0.27 & 0.17 & 0.27 & 0.15  \tabularnewline 
\tabularnewline 
 & \textbf{adaptive} & \textbf{self-adjust} & \textbf{self-generat} & \textbf{detect} & \textbf{independent} & \textbf{motor} & \textbf{engine} & \textbf{communicat} & \textbf{semi-conductor} & \textbf{semiconductor}  \tabularnewline 
\midrule 
Accuracy & 0.76 & 0.75 & 0.76 & 0.71 & 0.66 & 0.73 & 0.68 & 0.73 & 0.75 & 0.70  \tabularnewline 
Precision & 0.50 & 0.00 & 1.00 & 0.42 & 0.29 & 0.42 & 0.24 & 0.43 & 0.17 & 0.27  \tabularnewline 
Recall & 0.05 & 0.00 & 0.01 & 0.50 & 0.30 & 0.34 & 0.15 & 0.45 & 0.01 & 0.14  \tabularnewline 
F-measure & 0.09 & NaN & 0.02 & 0.46 & 0.29 & 0.38 & 0.19 & 0.44 & 0.02 & 0.19  \tabularnewline 
AUC & 0.52 & 0.50 & 0.50 & 0.64 & 0.54 & 0.60 & 0.50 & 0.63 & 0.50 & 0.51  \tabularnewline 
Matthew's C.C. & 0.09 & -0.05 & 0.09 & 0.27 & 0.07 & 0.21 & 0.00 & 0.26 & -0.02 & 0.03  \tabularnewline 
\tabularnewline 
 & \textbf{chip} & \textbf{bus} & \textbf{circuit} & \textbf{circuitry} & \textbf{antigen} & \textbf{antigenic} & \textbf{chromatography} & \textbf{Bessen-Hunt} & \textbf{Always 'No'} & \textbf{Always 'Yes'}  \tabularnewline 
\midrule 
Accuracy & 0.69 & 0.68 & 0.66 & 0.74 & 0.75 & 0.76 & 0.71 & 0.78 & 0.76 & 0.24  \tabularnewline 
Precision & 0.20 & 0.33 & 0.36 & 0.41 & 0.00 & 0.00 & 0.10 & 0.57 & NaN & 0.24  \tabularnewline 
Recall & 0.10 & 0.30 & 0.53 & 0.19 & 0.00 & 0.00 & 0.03 & 0.29 & 0.00 & 1.00  \tabularnewline 
F-measure & 0.13 & 0.31 & 0.43 & 0.26 & NaN & NaN & 0.04 & 0.38 & NaN & 0.39  \tabularnewline 
AUC & 0.49 & 0.55 & 0.62 & 0.55 & 0.49 & 0.50 & 0.47 & 0.61 & 0.50 & 0.50  \tabularnewline 
Matthew's C.C. & -0.04 & 0.11 & 0.21 & 0.14 & -0.07 & -0.04 & -0.09 & 0.28 & NaN & NaN  \tabularnewline 
\bottomrule 
\end{tabular} 
\begin{tablenotes}
\small
\item\textit{Note:} Every column is a different classification algorithms.
\item F-measure: balanced F-measure which is the evenly weightened harmonic mean between Precision and Recall. 
\item AUC: Area under (the receiver operating) curve.
\item Matthew's C.C.: Matthew's correlation coefficient.
\item\textit{Source:} USPTO, Google and own calculations.
\end{tablenotes}
\end{threeparttable}
\end{small}
\end{table}

>>>>

\begin{table}
\begin{small}
\begin{threeparttable}
\caption{{\normalsize Evaluation of different classification algorithms}}
\label{table:table_compare_classalg}
\begin{tabular}{rllllllllll}
\toprule 
 & \textbf{automat$_{t+a}$} & \textbf{robot$_{t+a}$} & \textbf{movable arm$_{t+a}$} & \textbf{algorithm$_{t+a}$} & \textbf{manual$_{t+a}$} & \textbf{software$_{t+a}$} & \textbf{computer$_{t+a}$} & \textbf{program$_{t+a}$} & \textbf{digital$_{t+a}$} & \textbf{autonomous$_{t+a}$}  \tabularnewline 
Accuracy & 0.78 & 0.76 & 0.76 & 0.76 & 0.77 & 0.77 & 0.77 & 0.78 & 0.76 & 0.76  \tabularnewline 
Precision & 0.83 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 0.62 & 0.79 & 0.47 & NaN  \tabularnewline 
Recall & 0.10 & 0.02 & 0.01 & 0.02 & 0.03 & 0.03 & 0.08 & 0.10 & 0.08 & 0.00  \tabularnewline 
F-measure & 0.17 & 0.04 & 0.02 & 0.04 & 0.06 & 0.06 & 0.14 & 0.18 & 0.13 & NaN  \tabularnewline 
AUC & 0.54 & 0.51 & 0.50 & 0.51 & 0.51 & 0.51 & 0.53 & 0.55 & 0.52 & 0.50  \tabularnewline 
MCC & 0.23 & 0.12 & 0.09 & 0.12 & 0.15 & 0.15 & 0.15 & 0.23 & 0.11 & NaN  \tabularnewline 
Number "Yes" & 12 & 2 & 1 & 2 & 3 & 3 & 13 & 14 & 17 & 0  \tabularnewline 
\tabularnewline 
 & \textbf{adaptive$_{t+a}$} & \textbf{self-adjust$_{t+a}$} & \textbf{self-generat$_{t+a}$} & \textbf{detect$_{t+a}$} & \textbf{independent$_{t+a}$} & \textbf{motor$_{t+a}$} & \textbf{engine$_{t+a}$} & \textbf{communicat$_{t+a}$} & \textbf{semi-conductor$_{t+a}$} & \textbf{semiconductor$_{t+a}$}  \tabularnewline 
Accuracy & 0.76 & 0.76 & 0.76 & 0.77 & 0.75 & 0.76 & 0.75 & 0.75 & 0.76 & 0.73  \tabularnewline 
Precision & 0.50 & 0.00 & 1.00 & 0.62 & 0.38 & 0.50 & 0.31 & 0.41 & 0.00 & 0.07  \tabularnewline 
Recall & 0.01 & 0.00 & 0.01 & 0.12 & 0.05 & 0.09 & 0.05 & 0.09 & 0.00 & 0.01  \tabularnewline 
F-measure & 0.02 & NaN & 0.02 & 0.21 & 0.08 & 0.15 & 0.08 & 0.14 & NaN & 0.02  \tabularnewline 
AUC & 0.50 & 0.50 & 0.50 & 0.55 & 0.51 & 0.53 & 0.51 & 0.52 & 0.50 & 0.49  \tabularnewline 
MCC & 0.04 & -0.03 & 0.09 & 0.20 & 0.06 & 0.13 & 0.03 & 0.09 & -0.04 & -0.07  \tabularnewline 
Number "Yes" & 2 & 1 & 1 & 21 & 13 & 18 & 16 & 22 & 2 & 14  \tabularnewline 
\tabularnewline 
 & \textbf{chip$_{t+a}$} & \textbf{bus$_{t+a}$} & \textbf{circuit$_{t+a}$} & \textbf{circuitry$_{t+a}$} & \textbf{antigen$_{t+a}$} & \textbf{antigenic$_{t+a}$} & \textbf{chromatography$_{t+a}$} & \textbf{Bessen-Hunt} & \textbf{Always "No"} & \textbf{Always "Yes"}  \tabularnewline 
Accuracy & 0.76 & 0.75 & 0.71 & 0.75 & 0.76 & 0.76 & 0.76 & 0.78 & 0.76 & 0.24  \tabularnewline 
Precision & 0.43 & 0.31 & 0.25 & 0.33 & NaN & NaN & 1.00 & 0.57 & NaN & 0.24  \tabularnewline 
Recall & 0.03 & 0.05 & 0.10 & 0.03 & 0.00 & 0.00 & 0.01 & 0.29 & 0.00 & 1.00  \tabularnewline 
F-measure & 0.05 & 0.08 & 0.14 & 0.05 & NaN & NaN & 0.02 & 0.38 & NaN & 0.39  \tabularnewline 
AUC & 0.51 & 0.51 & 0.50 & 0.51 & 0.50 & 0.50 & 0.50 & 0.61 & 0.50 & 0.50  \tabularnewline 
MCC & 0.06 & 0.03 & 0.01 & 0.03 & NaN & NaN & 0.09 & 0.28 & NaN & NaN  \tabularnewline 
Number "Yes" & 7 & 16 & 40 & 9 & 0 & 0 & 1 & 53 & 0 & 438  \tabularnewline 
\bottomrule 
\end{tabular} 
\begin{tablenotes}
\small
\item\textit{Note:} Every column is a different classification algorithms.
\item F-measure: balanced F-measure which is the evenly weightened harmonic mean between Precision and Recall. 
\item AUC: Area under (the receiver operating) curve.
\item MCC: Matthew's correlation coefficient.
\item\textit{Source:} USPTO, Google and own calculations.
\end{tablenotes}
\end{threeparttable}
\end{small}
\end{table}
